\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{hyperref, amssymb, amsmath, graphicx, subfigure}

\setlength{\oddsidemargin}{.25in}
\setlength{\evensidemargin}{.25in}
\setlength{\textwidth}{6in}
\setlength{\topmargin}{-0.4in}
\setlength{\textheight}{8.5in}

\setlength{\parindent}{0in}
\setlength{\parskip}{8pt}

\newcommand{\heading}[6]{
  \renewcommand{\thepage}{#1-\arabic{page}}
  \noindent
  \begin{center}
  \framebox{
    \vbox{
      \hbox to 5.78in { \textbf{#2} \hfill #3 }
      \vspace{4mm}
      \hbox to 5.78in { {\Large \hfill #6  \hfill} }
      \vspace{2mm}
      \hbox to 5.78in { \textit{Instructor: #4 \hfill #5} }
    }
  }
  \end{center}
  \vspace*{4mm}
}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{assumption}[theorem]{Assumption}

\newenvironment{proof}{\noindent{\bf Proof:} \hspace*{1mm}}{
  \hspace*{\fill} $\Box$ }
\newenvironment{proof_of}[1]{\noindent {\bf Proof of #1:}
  \hspace*{1mm}}{\hspace*{\fill} $\Box$ }
\newenvironment{proof_claim}{\begin{quotation} \noindent}{
  \hspace*{\fill} $\diamond$ \end{quotation}}
  
\newcommand{\lecture}[4]{\heading{#1}{ECE4880J: Computer Vision}{#2}{Siheng Chen}{#4}{#3}}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PLEASE MODIFY THESE FIELDS AS APPROPRIATE:
\newcommand{\lecturenum}{X} % lecture number
\newcommand{\lecturedate}{May 9, 2022} % date of lecture (e.g., 'March 20, 2010')
\newcommand{\lecturetitle}{Homework 1: Warm Up} % lecture title
\newcommand{\scribename}{{\bf YOUR NAME}} % full name of scribe
% PUT HERE ANY PACKAGES, MACROS, etc., ADDED BY YOU
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\lecture{\lecturenum}{\lecturedate}{\lecturetitle}{\scribename}


\section*{Instruction}

\begin{itemize}
    \item This homework is due at 11:59:59 p.m. on ** May 13th, 2022.
    \item The write-up must be an electronic version edited by LATEX.
    \item {\bf You will get the full credit once you submit your assignment on time.}
\end{itemize}


\section*{Q1. Let us know about you}
\begin{itemize}
    \item What is the most exciting experience at Shanghai Jiao Tong University?
    
    \item What is your favorite course at college so far? And why? 

    \item What is the most difficult thing you've encountered in life? How do you handle that situation?

    \item  How would you describe your ability in mathematics?

    \item  How would you describe your ability in programming?

    \item  How would you describe yourself as a team member?

    \item  Have you ever failed your partners in any project? If yes, how are you going to fix this in the future?

    \item  Are you fully prepared to take responsibility in the project of this course?

    \item Anything else you want to talk about yourself?
\end{itemize}

\section*{Q2. What do you think about computer vision}
\begin{itemize}
    \item Why do you choose this computer vision course expect for the course credits?
    
    \item What is the coolest computer-vision-related application for you?

    \item Is there any specific computer vision technique you are eager to know? 

    \item Do you have experience in computer vision?

    \item Do you expect doing research on computer vision or working on computer-vision-related jobs in your career? If yes, could you describe your ideal work environment?

    \item Which computer vision topic do you want to learn from this course?

    \item Which track of the course project are you going to choose?

\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% bibliography goes here
\bibliographystyle{amsalpha}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%